### 2020-07-27 CILAMCE_2020/paper.tex
New todo
Add visualization section

% --------------------------------------------------------------------------
\subsection{Dataset} \label{subsec:dataset}
% --------------------------------------------------------------------------
The data was downloaded from the University of California Irvine website \cite{downloadData}. The same dataset used by \citet{Yeh1998} and the related works. In total there are 1030 rows with 9 columns. Each row represents a sample with the variables: compressive strength, age, and 7 ingredients (water, cement, fine aggregate, coarse aggregate, fly ash, blast furnace slag, and superplasticizers).

TODO: Possivel tabela das primeiras amostras aqui

@@

>>>>

% --------------------------------------------------------------------------
\subsection{Dataset} \label{subsec:dataset}
% --------------------------------------------------------------------------
The data was downloaded from the University of California Irvine website \cite{downloadData}. The same dataset used by \citet{Yeh1998} and the related works. In total there are 1030 rows with 9 columns. Each row represents a sample with the variables: compressive strength, age, and 7 ingredients (water, cement, fine aggregate, coarse aggregate, fly ash, blast furnace slag, and superplasticizers). TODO: referencia link do github com o arquivo xls utilizado (os dados originais)

@@

Several plots and tables were built to perform the visualization of the samples prepared in the previous step. Including analysis of the descriptive statistics of the continuous and categorical variables, the distribution of the variables in relation to the compressive strength, the correlation between the variables grouped by age, the relationship between the approximate mix and the compressive strength, the relationships between the main concrete ingredients and the compressive strength and principal component analysis (PCA) of the ingredients. All of these plots/tables are part of the extended version available on github. (TODO: reference). However, to keep the article short, here only the plots of the statistical analysis of the categorical variables are presented, which are used for an insight in the conclusion of this work.

\begin{figure}[!ht]
\begin{center}
\includegraphics[scale=0.8]{Figures/stat-summ-categorical.pdf}
\vspace{12pt}
\caption{Descriptive statistics of the categorical variables}
\label{fig:categorical}
\end{center}
\end{figure}
\vspace{8pt}
